Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
update citation

We use the statistical programming language R [@citeR].

>>>>

Our analysis was conducted using R [@citeR] along with several supporting packages. We used the **tidyverse** for data manipulation [@tidyverse], **readr** for data import [@readr], and **here** for file management [@here].

Dynamic reporting was handled with **knitr** [@knitr], while **kableExtra** allowed for enhanced table formatting [@kableExtra]. We used **scales** to adjust visualization scales [@scales], and **arrow** for efficient data processing [@arrow].

For Bayesian modeling and visualization, we used **bayesplot** [@bayesplot] and **rstanarm** [@rstanarm].
